Data Specialization for a Staged Lambda Calculus

### 2015-02-10 paper/figures/splitting-overview.tex
fixes to figures
fixed figures

\hspace{2em} Evaluation Rule: $\sepredtwo {\pipeM c l r} {\mval i {[b/l]r}}$, where $b$ (also the {\em boundary value}) is generated by $\reduce c (i,b)$

@@

\put(14,75){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$\colone e A$}}}
\put(14,37){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$[\xi,v]$}}}
\put(64,75){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$\pipeM c l r$}}}
\put(64,37){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$\mval i q$}}}

>>>>

\hspace{2em} Evaluation Rule: $\sepredtwo {\pipeM c l r} {\mval i {[b/l]r}}$, where $b$ (also called the {\em boundary value}) is generated by $\reduce c {\tup{i,b}}$

@@

\put(14,75){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$\colmix e A$}}}
\put(14,37){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$[\xi,v]$}}}
\put(64,75){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$\pipeM c l r$}}}
\put(64,37){\raisebox{-0.5ex}{\makebox[22 \unitlength]{$\mval i q$}}}
